\textbf{NBA Party}

### 2017-04-11 init_model.rnw
Brought in population data.

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/nmusician_estabs.RData')

>>>>

load(file = 'tmp_data/covers_lines.RData')
load(file = 'tmp_data/nmusician_estabs.RData')
load(file = 'tmp_data/population_by_county_year.RData')

musicians <- merge(musicians, pop, by = c('county', 'season'), all.x = T)
